%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt, a4paper]{awesome-cv}

\fontdir[fonts/]
\colorlet{awesome}{awesome-emerald}

% Datos personales
\name{Oscar David}{Hernández Rodríguez}
\email{oscarhe@ciencias.unam.mx}
\mobile{(477) 760-8225}
\github{OscarHeRo}
\linkedin{oscar-hernández-460a481a2}
\position{Computer Science Student}

\begin{document}

\makecvheader

\recipient
  {SAP Recruiting Team}
  {SAP Mexico\\Mexico City or Monterrey}
\letterdate{\today}
\lettertitle{Application for SAP Training and Adoption Intern}
\letteropening{Dear SAP Recruiting Team,}

\begin{cvletter}
I am a Computer Science student with strong analytical and communication skills, eager to contribute to SAP’s Training and Adoption initiatives. With experience in user support, data analysis, and technical documentation, I thrive in environments that require clarity, collaboration, and adaptability.

In past roles, I have worked directly with students and users, designed onboarding materials, and supported team coordination and process tracking. I am fluent in English and Spanish and have a working knowledge of Portuguese. My academic background includes data-driven coursework and project experience using tools such as Excel, SQL, Python, and R.

I am especially drawn to SAP’s focus on collaboration, global impact, and continuous learning. I am excited about the opportunity to work with diverse teams, help customers build effective learning journeys, and contribute to the success of SAP Learning Hub and its related initiatives.

Thank you for considering my application. I look forward to the opportunity to bring my energy and commitment to SAP’s Training and Adoption team.
\end{cvletter}

\letterclosing{Sincerely,}

\makeletterclosing

\end{document}