\cvsection{Cover Letter}
\begin{cvparagraph}

    Dear Hiring Committee,


My name is \textbf{Oscar David Hernández Rodríguez}, and I’m a Computer Science student at the National Autonomous University of Mexico (UNAM), currently entering the final year of my degree. I’m writing to express my interest in the \textbf{Professional Services Intern} position in Mexico City.

I’ve spent the last few years immersed in computer science—coding, building, solving, and learning. But what has driven me most is the chance to work with others, to share ideas, and to build things that matter. That’s why this opportunity excites me: it brings together technical challenge, collaboration, and the kind of environment where I can keep growing.

In my academic journey, I’ve led development projects, explored systems like compilers and concurrent programming, and helped others as a teaching assistant. These experiences have taught me how to think formally, solve problems under pressure, and communicate clearly. I believe those same skills can help me contribute to real-world AWS projects.

This summer, I’ll be available full-time—and I see this internship as the perfect way to bridge what I’ve learned in theory with how things are built in practice. I want to be part of a team where I can learn from professionals and help create solutions that scale and serve.


Thank you for considering my application. I’d be honored to collaborate with AWS and give my full commitment to this opportunity.

Sincerely,  
\textbf{Oscar David Hernández Rodríguez}  \\
(oscarhe@ciencias.unam.mx)

\end{cvparagraph}
